Stack Safety as a Security Property

### 2021-04-23 submission2/example2.tex
Moved tex/ to submission2/

\begin{figure}[b]
    \begin{minipage}{.35\textwidth}
\begin{verbatim}
int main() {
  long int x = 42, y = 0;
  print &y;
  y = f(x);
  return y;
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.35\textwidth}
\begin{verbatim}
long int f(long int z) {
  print g();
  return (z+z);
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.25\textwidth}
\begin{verbatim}
int g() {
  return 5;
}
\end{verbatim}
    \end{minipage}
\caption{A Simple Call}
\label{fig:share-program}
\end{figure}

>>>>

\begin{figure}[b]
    \begin{minipage}{.35\textwidth}
\begin{verbatim}
int main() {
  int x = 42, y = 0;
  swap(&x,&y);
  return y;
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.35\textwidth}
\begin{verbatim}
void swap(int* a, int* b) {
  int tmp = *a;
  *a = *b;
  *b = tmp;
  print g();
  return (z+z);
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.25\textwidth}
\begin{verbatim}
int g() {
  return 5;
}
\end{verbatim}
    \end{minipage}
\caption{A Simple Call}
\label{fig:share-program}
\end{figure}
